Make any stupid plot you want

### 2021-02-14 draft/sections/intro.tex
trying to compile next + fixed some errors

\documentclass[../main.tex]{subfiles}
\begin{document}
\section{Introduction}
\label{sec:intro}
"We have a unified mathematical description of understanding visualization.  Lots of people have worked on this and each has identified and described important aspects, but each has specialized in some way and it is not clear how to align them.  We can understand all of the prior work via our framework that pulls from {established math}"
that way you make clear what your contribution is, gives you a context to bring up all of the citations, a frame to contrast them, and then a nice lead into the math
I like your framing
and "we validate the framework by using it to re-design artist and data access layer of Maptlotlib, a general purpose visualization tool"

@@

As described by Mackinlay, a visualization tool produces a graphical design and an image rendered based on that design. He defines the graphical design as the set encoding relations from data to visual representation\cite{mackinlayAutomatingDesignGraphical1986}, and the design rendered in an idealized abstract space is what throughout this paper we will refer to as a graphic. Mackinlay  proposes that a visualization tool's expressiveness is a measure of how much of the structure of the data the tool encodes, while the tools effectiveness describes how much design choices are made in deference to perceptual saliency \cite{clevelandResearchStatisticalGraphics1987,clevelandGraphicalPerceptionTheory1984,chambersGraphicalMethodsData1983a, munznerVisualizationAnalysisDesign2014}. Mackinlay's definition of expressiveness is formalized at the visual encoding level, which as shown in figure~\ref{fig:intro_retinal_variables} refers to the components of a graphic such as the color or position of a glyph. Bertin first classified these graphic components as retinal variables and discussed which types of data they can express \cite{bertinIIPropertiesGraphic2011} and how they are composited on point, line, and area graphical marks, as shown in figure~\ref{fig:intro_retinal_variables} correspond. Marks can be generalized to glyphs, which are graphical objects that convey one or more attributes of the data entity mapped to it\cite{ware2019information}. Mackinlay's expressiveness criteria is well defined for the visual variables, such that he suggests the viability of a strict encoding relation that is a homomorphic mapping which preserves some binary operator from one domain to another \cite{mackinlayAUTOMATICDESIGNGRAPHICAL1987}. We expand on this suggestion by proposing that monoid action equivariance is a strict condition of building valid encoders. Mackinlay does not provide a generalized criteria for plot types, instead embedding the requirements within the definition of the charts.

>>>>

\documentclass[../main.tex]{subfiles}
\begin{document}
\section{Introduction}
\label{sec:intro}
"We have a unified mathematical description of understanding visualization.  Lots of people have worked on this and each has identified and described important aspects, but each has specialized in some way and it is not clear how to align them.  We can understand all of the prior work via our framework that pulls from {established math}"
that way you make clear what your contribution is, gives you a context to bring up all of the citations, a frame to contrast them, and then a nice lead into the math
 "we validate the framework by using it to re-design artist and data access layer of Maptlotlib, a general purpose visualization tool"

@@

As described by Mackinlay, a visualization tool produces a graphical design and an image rendered based on that design. He defines the graphical design as the set encoding relations from data to visual representation\cite{mackinlayAutomatingDesignGraphical1986}, and the design rendered in an idealized abstract space is what throughout this paper we will refer to as a graphic. Mackinlay  proposes that a visualization tool's expressiveness is a measure of how much of the structure of the data the tool encodes, while the tools effectiveness describes how much design choices are made in deference to perceptual saliency \cite{clevelandResearchStatisticalGraphics1987,clevelandGraphicalPerceptionTheory1984,chambersGraphicalMethodsData1983a, munznerVisualizationAnalysisDesign2014}. Mackinlay's definition of expressiveness is formalized at the visual encoding level, which as shown in figure~\ref{fig:intro_retinal_variables} refers to the components of a graphic such as the color or position of a glyph. Bertin first classified these graphic components as retinal variables and discussed which types of data they can express \cite{bertinIIPropertiesGraphic2011} and how they are composited on point, line, and area graphical marks, as shown in figure~\ref{fig:intro_retinal_variables} correspond. Marks can be generalized to glyphs, which are graphical objects that convey one or more attributes of the data entity mapped to it\cite{ware2019information, munznerVisualizationAnalysisDesign2014}. Mackinlay's expressiveness criteria is well defined for the visual variables, such that he suggests the viability of a strict encoding relation that is a homomorphic mapping which preserves some binary operator from one domain to another \cite{mackinlayAUTOMATICDESIGNGRAPHICAL1987}. We expand on this suggestion by proposing that monoid action equivariance is a strict condition of building valid encoders. Mackinlay does not provide a generalized criteria for plot types, instead embedding the requirements within the definition of the charts.

### 2021-02-14 draft/sections/math.tex
trying to compile next + fixed some errors

\begin{figure}
    \includegraphics[width=\textwidth]{figures/math/graphic_render.png}
    \caption{To render a graphic, a pixel $p$ is selected in the display space, which is defined in the same coordinates as the x and y components in \gfiber\.  The inverse mapping ${\gsection_{xy}}^(p)$ returns a region $\gbase_{p} \subset \gbase$. $\gsection(\gbase_{p})$ returns the list of elements $(x,\,y,\,r,\,g,\,b) \in \gfiber$ that lie over $\gbase_{p}$. The integral over the $(r,\,g,\,b)$ elements is the color of the pixel.}
    \label{fig:graphic_rho_lookup}
\end{figure}
As shown in figure~\ref{fig:graphic_rho_lookup}, the output space queries into the graphic bundle to render the image. We select a pixel $p$ in the output space, inverse map the region of the pixel into $\gbase_p \subset \gbase$, then compute the section $gsection$ over the region $\gbase_p$. The section yields the set of elements in \gfiber\ that specify the $(r, g, b)$ values corresponding to the region $p$. The color of the pixel is then obtained by taking the integral of $\gsection_{rgb}(\gbase_p)$.

>>>>

\begin{figure}
    \includegraphics[width=\textwidth]{figures/math/graphic_render.png}
    \caption{To render a graphic, a pixel $p$ is selected in the display space, which is defined in the same coordinates as the x and y components in \gfiber\.  The inverse mapping ${\gsection_{xy}}^(p)$ returns a region $\gbase_{p} \subset \gbase$. $\gsection(\gbase_{p})$ returns the list of elements $(x,\,y,\,r,\,g,\,b) \in \gfiber$ that lie over $\gbase_{p}$. The integral over the $(r,\,g,\,b)$ elements is the color of the pixel.}
    \label{fig:graphic_rho_lookup}
\end{figure}
As shown in figure~\ref{fig:graphic_rho_lookup}, the output space queries into the graphic bundle to render the image. We select a pixel $p$ in the output space, inverse map the region of the pixel into $\gbase_p \subset \gbase$, then compute the section $\gsection$ over the region $\gbase_p$. The section yields the set of elements in \gfiber\ that specify the $(r, g, b)$ values corresponding to the region $p$. The color of the pixel is then obtained by taking the integral of $\gsection_{rgb}(\gbase_p)$.
